### 2024-08-30 mycv/subs/papers.tex
snapshot

  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
  {submitted}

@@

  {Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}
  {submitted}

@@

  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
  {submitted}

>>>>

  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
  {A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}

@@

  {\href{https://doi.org/10.1016/j.jma.2024.08.009}{Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}}
  {in-press}

@@

  {\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}}
  {Vol. 181, 104098, 2024}
  {\href{https://doi.org/10.1016/j.ijplas.2024.104032}{Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}}
  {Vol. 179, 104032, 2024}
